True versus apparent shapes of astrophysical bow shocks

### 2015-07-02 papers/Paper1/sec-intro.tex
Wrote something about bow shocks for intro

The archetypical bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.

@@

>>>>

The archetypal bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.
Instead of a solid body, astrophysical examples usually involve the
interaction of \emph{two} supersonic flows, such as the situation of a
stellar wind emitted by a star that moves supersonically through the
interstellar medium \citep{}.  In such cases, two shocks are generally
produced, one in each flow, and technically speaking only the shock in
the ambient medium is a ``bow shock'', whereas the other is the ``wind
shock'' or ``termination shock''.  However,

@@

%%
%% Effects of instabilities
%%
